# Results

```{r results preps}

results <- read_csv("results.csv")

results$BatchName <- factor(x = results$BatchName, levels = c("Netsize", "Addfriends", "Unfriend"))
results$ConfigAgentCount <- as.factor(results$ConfigAgentCount)
results$ConfigUnfriendThresh <- as.factor(results$ConfigUnfriendThresh)
results$ConfigAddfriendMethod <- factor(x = results$ConfigAddfriendMethod, 
                                        levels = c("neighborsofneighbors", "hybrid", "random"), 
                                        labels = c("neighbors", "hybrid", "random"))

levels(results$ConfigAddfriendMethod)[1] <- "neighbors"

results %>% 
   mutate(Xlabel = case_when(BatchName == "Addfriends" ~ as.character(ConfigAddfriendMethod),
                           BatchName == "Unfriend" ~ as.character(ConfigUnfriendThresh),
                           BatchName == "Netsize" ~ as.character(ConfigAgentCount)),
         Xlevel = case_when(BatchName == "Addfriends" ~ as.numeric(ConfigAddfriendMethod),
                           BatchName == "Unfriend" ~ as.numeric(ConfigUnfriendThresh),
                           BatchName == "Netsize" ~ as.numeric(ConfigAgentCount))) -> results

results %>% 
  filter(BatchName == "Netsize") %>% 
  select(-c(BatchName, ConfigUnfriendThresh, ConfigAddfriendMethod, Xlabel, Xlevel)) %>% 
  group_by(ConfigAgentCount) %>% 
  summarise_all(mean) -> netsize_aggregates

results %>% 
  filter(BatchName == "Addfriends") %>% 
  select(-c(BatchName, ConfigUnfriendThresh, ConfigAgentCount, Xlabel, Xlevel)) %>% 
  group_by(ConfigAddfriendMethod) %>% 
  summarise_all(mean) -> addfriends_aggregates

results %>% 
  filter(BatchName == "Unfriend") %>% 
  select(-c(BatchName, ConfigAddfriendMethod, ConfigAgentCount, Xlabel, Xlevel)) %>% 
  group_by(ConfigUnfriendThresh) %>% 
  summarise_all(mean) -> unfriend_aggregates
```

We performed in total 13 different simulation runs that cover the following variations of factor configuration:

- Network Size in 100, 200, 300, 400, 500 Agents
- Addfriends Method as Neighbors, hybrid and random
- Unfriend Threshold of 0.4, 0.6, 0.8, 1.0, 1.2

This allows us to examine subsequently the influence of the factor levels separately.
Each distinct simulation configuration was repeated 100 times to eliminate effects that are due to usage of random number generators in the simulations.
The results that are reported in the following are always averaged over the repetitions of a particular configuration run.

The influence of the factors was evaluated with various measures that can be classified into the following facets:

1) Degree Distribution
2) Centrality Measures
3) Community Measures
4) Opinion Dynamics
5) Supernode properties

Figure \@ref(fig:CombinedEval) shows the influence of each factor on one representative measure of those facets.
As can be seen, the network size did not affect the community structure and opinion dynamics significantly.
In comparison, the addfriends method had additional on the opinion dynamics and only the unfriend threshold showed influence on all facets. Subsequently, the particular effects are examined more detailed and seperately per factor.

```{r CombinedEval, fig.height=8, fig.width=8, fig.cap="Overview of the factor influences on exemplary measures of the analyzed facets."}
results %>% 
  select(BatchName, Densities,ClosenessCentralityMean, CommunityCountNontrivial, OpinionSD, SupernodeBetweenness, Xlabel, Xlevel) %>% 
  gather("key", "value", Densities, ClosenessCentralityMean, CommunityCountNontrivial, OpinionSD, SupernodeBetweenness) %>% 
  mutate(key = factor(key, levels = c("Densities", 
                                      "ClosenessCentralityMean", 
                                      "CommunityCountNontrivial", 
                                      "OpinionSD", 
                                      "SupernodeBetweenness"))) %>% 
  group_by(BatchName, Xlabel,key) %>%
  arrange(Xlevel) %>% 
  ggplot(aes(x=reorder(Xlabel, Xlevel), y=value)) +
  facet_grid(key~BatchName, scales = "free", switch = "y", labeller = label_wrap_gen(width=10)) +
  geom_violin(alpha = 0.1, fill = "black", color = "NA") +
  geom_boxplot(alpha = 0.5, aes(fill=Xlevel)) +
  theme(strip.text.y = element_text(angle = 180),
          axis.title.x = element_text(margin = margin(t = 20, r = 0, b = 0, l = 0)),
          axis.title.y = element_blank(),
          panel.spacing = unit(1, "lines")) +
  scale_y_continuous(position = "right") +
  labs(x="Factor level", title="Factor influence overview") +
  theme(legend.position = "none") +
  scale_fill_viridis_c()
```



## Impact of Network Size
<!-- In dem Unterkapitel springst du etwas zwischen den Zeiten, ich würde glaube ich alles im past schreiben -->
In our simulation, the size of a social network is especially influential for the deviation of network parameters and opinions throughout the members of a network.
While the density of a network decreases significantly from 10.3% in a network of 100 agents to 8.6% for n=200 and further on to 8.2% for n=500, the standard deviations of outdegree and indegree increase which shows that the preferential attachment algorithm overruns the pursuit of each agent to connect to one tenth of the network members.
In terms of network centrality, only the closeness centrality increases through more agents while betweenness and eigenvector centrality decrease.
This shows that while the agents' connectivity to each other agent in the network rises, the agents have on average less influence on their neighbors.

The influence and the outreach of the supernode in a network depends on the overall network size.
While in a network of 100 agents every third follows the supernode directly, this value increases continuously for networks with more agents.
In a network with 500 agents already every other agent is a follower of the supernode.
Regarding the other centrality measures, the supernode shows higher closeness centrality for larger networks, but lower betweenness and eigenvector centrality with higher network size.
This shows that while the supernode is more central in terms of connectedness to all other nodes, its importance as a connector between all other agents is decreasing.
The network size did not affect the opinion difference between the two agents with highest outdegrees as their opinions were always rather conform with each other.  
The network size did not influence the cluster and community structure within a network consistently.
The opinion dynamics did not differ significantly regarding network size either.
The opinion diversity in the network had a slight upgoing trend for larger networks.
The mean difference between an agent's own opinion and its perceived public opinion in the final state increased slightly with network size as well.

Most important outcomes:
- Density
- Supernode Outdegree
- Mean Betweenness Centrality

## Impact of the addfriends mechanic

The mechanic for adding new friends shows an influence for the network and the opinion distribution in it.
When picking new friends only from friends of current friends, the density of a network stays lower than for picking randomly from all agents in the network with regard to the opinion difference and for a hybrid approach of both methods.
While the standard deviations of outdegree and indegree for each agent to not differ significantly between the different approaches, the mean ratio between outdegree and indegree per agent is less balanced when agents only choose from neighbors of neighbors.

The least influence of the addfriends mechanic can be perceived in terms of network centrality of each agent.
Only the closeness centrality is slightly higher for the random and hybrid approach, while betweenness and eigenvector centrality do not show significant changes.
Concerning clustering and community structure, the clustering coefficient increases slightly by using the random approach while the number of communities is higher for networks where agents only pick neighbors of neighbors and also the number of disconnected communities is higher for this configuration.  
The node with the highest influence and outreach in the network is not affected by the addfriends mechanic.
The opinion difference of the two nodes with highest outdegree shows more extreme outliers for the random addfriends method but no significant difference to the other approaches.
The opinion distribution, on the opposite, is significantly higher if the agents only connect to others that are already in their indirect neighborhood.
The amount of opinion changes per agent is slightly higher when agents pick their new friends randomly and according to the opinion difference.
Looking on the distance between perceived public and own opinion in the final state, those two values are significantly closer to each other when the random or hybrid approach for choosing new friends is used.

-

## Impact of Unfriend Threshold

The threshold of an agent to accept diverging opinions was influential for both the network structure and the opinion distribution in a network.
If the agents in a network are more tolerant in keeping friendships, the density of the network increases significantly and with it also the variety of outdegrees and indegrees within the network members.
The ratio between outdegree and indegree gets more balanced for networks of agents with higher opinion tolerance.

The centrality of each agent in the network changes with the unfriend threshold as closeness and eigenvector centrality increase with higher tolerance of friends with diverging opinions. The betweenness in contrast decreases with a rising threshold.
The clustering and community measures show that while clustering increases through higher unfriend thresholds, the number of separate communities detected through label propagation decreases.

The role of the agent with the highest follower count also depends on the unfriend threshold.
While outdegree and closeness centrality stay rather equal for a threshold from 0.4 to 1.0, in a network with unfriend threshold of 1.2, both values increase significantly.
So the supernode profits only in terms of post reach when every agent is very tolerant with keeping fellowships that bear a high opinion difference. 
The betweenness and eigenvector centrality decrease continuously with rising unfriend threshold, but this trend seems to turn around at least for the eigenvector centrality with an unfriend threshold of 1.2.
Comparing the opinion of the most important and second most important agent we observe a significantly higher difference for unfriend thresholds of 0.8 and 1.2 whereas for the lower and higher thresholds the opinions of them is close to each other.  
With changing the unfriend threshold it is possible to subsequently influence the opinion distribution within the network.
While in networks with low threshold the standard deviation of opinions is below 0.1 on average, this measure rises notably up to 0.5 for a network with an unfriend threshold of 0.6 and even continues with higher thresholds to 0.6 for a threshold of 1.2.
Meanwhile, the mean delta between initial and final opinion of all agents in the networks shows the opposite trend.
While the opinion change is with 0.5 rather large for thresholds below or equal to 0.6, it falls below 0.3 for networks with a larger threshold.
The least opinion change occurs for a threshold of 1.0 while with 1.2 the opinion change starts to increase again.
With rising unfriend threshold also the distance between perceived public and own opinion increases significantly.

- Density
- Closeness Centrality
- Community Count nontrivial
- Opinion SD
- Opinion Change
- Opinion Difference 1st 2nd supernode
